Partial Least Squares Regression with Multiple Functional and Scalar Predictors

### 2025-08-12 manuscript/aoas-sample.tex
geometric property start

%custom packages
 \usepackage{algorithm}
 \usepackage[noend]{algpseudocode}
 \usepackage{hyperref}
 \usepackage{enumerate}

% \usepackage{url} % not crucial - just used below for the URL 
% \usepackage{bibunits}
\usepackage{subcaption}
% \usepackage{adjustbox}
\usepackage{verbatim} % to comment out

@@

% \usepackage{bm}
% \usepackage{multirow,multicol}
% \usepackage{verbatim}
% \usepackage{amsfonts,amssymb,amsthm,color,authblk}
% \usepackage{xcolor}
% \definecolor{myblue}{RGB}{0, 0, 0}
% \newcommand{\blue}[1]{{\color{myblue}#1}}
\startlocaldefs
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Uncomment next line to change            %%
%% the type of equation numbering           %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\numberwithin{equation}{section}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% For Axiom, Claim, Corollary, Hypothesis, %%
%% Lemma, Theorem, Proposition              %%
%% use \theoremstyle{plain}                 %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\theoremstyle{plain}
\newtheorem{axiom}{Axiom}
\newtheorem{claim}[axiom]{Claim}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% For Assumption, Definition, Example,     %%
%% Notation, Property, Remark, Fact         %%
%% use \theoremstyle{definition}            %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem*{example}{Example}
\newtheorem*{fact}{Fact}
\newtheorem{remark}{Remark}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Please put your definitions here:        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}

@@

\section{Proposed PLS Algorithm} \label{sec: Proposed PLS Algorithm}
To address the limitations outlined in Section \ref{sec: Naive PLS Algorithm}, we propose  novel strategies for implementing the steps of the hybrid PLS algorithm. Our approach provides an efficient and robust means of producing PLS components and scores in the presence of multiple dense and/or irregular functional predictors and scalar predictors. It also incorporates a regularization scheme that enables the algorithm to borrow strength and exploit structural relationships within and between the functions to avoid overfitting of the PLS components and to improve the generalizability and interpretability of the predictive model.
Each iteration of our approach consists of two subroutines: regularized estimation of smoothed PLS components and orthogonalization, detailed in Sections~\ref{subsec: Step 1: Computing Smoothed PLS components} and~\ref{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression}, respectively. After a suitable number of iterations, the hybrid regression coefficient is estimated, as described in Section~\ref{subsec: Obtaining the Estimated Hybrid Regression Coefficient}. For notational simplicity, we omit the iteration index $l$ in the following discussion, with the understanding that the subroutines apply to any iteration. The complete algorithm is summarized in Algorithm~\ref{alg:main}.

\subsection{Preliminary step: Finite-basis Approximation }\label{sec: finite basis approximation}	

@@

\subsection{Step 1: Computing smoothed PLS component direction}  \label{subsec: Step 1: Computing Smoothed PLS components} 
We begin with the first step of the iterative algorithm: estimating the smooth PLS component direction. Section~\ref{sec: pls component computation intermediate} introduces the core optimization problem for this step, formulated as a generalized Rayleigh quotient. Building on this, Section~\ref{sec: Regularization of PLS Components} presents a modified version that promotes smoothness, which is the estimation procedure for our proposed method, along with a efficient computation scheme.

\subsubsection{Core optimization problem for PLS component direction estimation}\label{sec: pls component computation intermediate}
Building on the basis function approximation in Section~\ref{sec: finite basis approximation}, we now present the core optimization problem that directly estimates the hybrid PLS component direction. This strategy fully leverages the continuous nature of the functional components and the function-scalar hybrid structure, and can be implemented using simple matrix-vector multiplications.

We describe the strategy at the $l$-th iteration. %For simplicity, we omit the iteration index and assume the observations have been residualized from previous steps (see Section~\ref{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression} for details). 
The  PLS component direction is estimated by the unit-norm direction $\xi^{[l]} \in \widetilde{\mathcal{H}}$ that maximizes the squared empirical covariance, which quantifies the linear dependence between the PLS scores $\langle \widetilde{W}_1, \xi \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$, defined as

@@

\subsubsection{Proposed Approach: Regularized and Smoothed Computation} \label{sec: Regularization of PLS Components}
Although Proposition \ref{proposition:eigen_noregul} efficiently estimates the PLS component direction $\hat{\xi} = (\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\zeta}})$, the functional components $\hat{\xi}_1, \ldots, \hat{\xi}_K$ may not be smooth, potentially leading to overfitting and unstable predictions. To address this, we propose a regularized extension that balances predictive performance with smoothness. Specifically, we penalize the roughness of each $\hat{\xi}_j$ using its integrated squared second derivative 
\begin{equation}\label{def:roughness_penalty}
	\operatorname{PEN}(\hat{\xi}_j) := \int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
	.
\end{equation}

@@

\medskip
\noindent
\textit{Proposed estimation procedure.}~
To avoid the orthogonal basis assumption of  \citet{Rice1991}, we adopt the strategy of \citet{Silverman1996}, which replaces the standard orthonormality constraint with a weaker one based on a modified inner product that incorporates roughness. Accordingly, our estimation procedure at the $l$-th iteration, iteration index omitted and assuming the observations have been residualized in previous steps, solves the following optimization problem:
\begin{equation}\label{def:maximizer_squared_empirical_cov_reg}
	\hat{\xi} 
	= 
	(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\zeta}}
	)
	:= \arg \max_{\xi \in \widetilde{\mathcal{H}}
	}~\widehat{\textnormal{Cov}}^2 
	\bigl(
	\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
	\bigr)~s.t.~\| \xi  \|_\mathcal{H} +  \sum \limits_{j=1}^K \lambda_j 
	\operatorname{PEN}(\xi_K) = 1.
\end{equation}
This formulation maximizes the squared covariance over a class of smooth functions.
Proposition~\ref{proposition:eigen_regul} expresses this problem as a generalized Rayleigh quotient.

@@

\subsection{Step 2: Computing Residualized Predictors via Hybrid-on-Scalar Regression} \label{subsec: Step 2: Computing Predictors via Hybrid-on-Scalar Regression}
The $l$-th iteration's second step involves residualization of both predictors and responses. We first compute the individual PLS score:  
\begin{equation}\label{def:plsscore}
	\hat{\rho}^{[l]}_i := \langle \widetilde{W}_i^{[l]}, \, \hat{\xi}^{[l]} \rangle_{\mathcal{H}},
\end{equation}
using the estimated PLS component direction $\widehat{\xi}^{[l]}$ obtained from Propositions \ref{proposition:eigen_regul} and \ref{proposition:linear_regul}. 
Since   $\widetilde{W}_i^{[l]}$ are assumed to have a sample mean of zero, these PLS scores will also have a sample mean of zero.
Using these PLS scores as scalar predictor observations, the $(l+1)$-th iteration's residualized response is computed as:
\begin{equation}\label{algorithm_step:residualization_response}
	Y_i^{[l+1]} := Y_i^{[l]} - 
	\frac{
		( \mathbf{y}^{[l]} )^\top  \hat{\boldsymbol{\rho}}^{[l]}
	}{
		( \hat{\boldsymbol{\rho}}^{[l]} )^\top  \hat{\boldsymbol{\rho}}^{[l]}
	}
	\widehat{\rho}_{il},
\end{equation}
which is equivalent to using the least squares estimate from regressing $Y_i^{[l]}$ on $\widehat{\rho}_{il}$,
a procedure identical to that found in the naive PLS algorithm (Section \ref{sec: Naive PLS Algorithm}). 
Since $Y_i^{[l]}$ are assumed to have a sample mean of zero, these residuals $Y_i^{[l+1]}$   also have a sample mean of zero.

@@

\begin{lemma}[Closed-form  solution]\label{proposition:closed_form_orthgonalization}
	Let us denote
	$
	\hat{\boldsymbol{\rho}}^{[l]} := (\hat{\rho}^{[l]}_1, \ldots, \hat{\rho}^{[l]}_n)^\top.
	%\quad\text{and} \quad		\bar{\rho}^{[l]} := (\hat{\boldsymbol{\rho}}^{[l]})^\top \hat{\boldsymbol{\rho}}^{[l]}.
	$
	The solution to the optimization problem \eqref{def:argmin_pensse}, denoted
	$\hat{\delta}^{[l]}   \in \tilde{\mathcal{H}}$, has basis coefficients and scalar parts given by:
	\begin{equation*}
		\hat{\boldsymbol{\pi}}_j^{[l]}
		=
		\bigl(
		\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2
		B
		+
		\tau
		B^{\prime \prime}
		\bigr)^{-1}
		B
		(\Theta_j^{[l]})^\top
		\hat{\boldsymbol{\rho}}^{[l]}
		,
		~
		j = 1, \ldots, K,
		%%%%%%%%%%%%%%%%%%%%%%%%
		\quad
		\hat{\boldsymbol{\chi} }^{[l]}
		=
		(\mathbf{Z}^{[l]})^\top  \hat{\boldsymbol{\rho}}^{[l]}.
	\end{equation*}
\end{lemma}
Proof of Lemma \ref{proposition:closed_form_orthgonalization} is provided in Appendix \ref{section:proof:proposition:closed_form_orthgonalization}.

@@

\subsection{Obtaining the Estimated Hybrid Regression Coefficient}
\label{subsec: Obtaining the Estimated Hybrid Regression Coefficient}
The regression coefficient $\boldsymbol{\eta}$ in model \eqref{eq: Hybrid functional model} can be written in terms of the estimated PLS components and scores. First, note that we can show $\widehat{\rho}_{il} = \langle \mathbf{W}_i^{[l]}, \widehat{\xi}_l \rangle_\mathcal{H} = \langle \mathbf{W}_i, \widehat{\boldsymbol{\zeta}}_l \rangle_\mathcal{H}$, where $\widehat{\boldsymbol{\zeta}}_l = \widehat{\xi}_l - \sum_{u=1}^{l-1} \langle \widehat{\boldsymbol{\delta}}_u, \widehat{\xi}_l \rangle_{\mathcal{H}} \widehat{\boldsymbol{\zeta}}_u$ for $l \ge 2$, with $\widehat{\boldsymbol{\zeta}}_1 = \widehat{\xi}_1$. Then, the decomposition of $Y_i$ in \eqref{eq: decomposition} leads to
\begin{equation*}
	Y_i = \sum \limits_{l=1}^L \widehat{\nu}_l \langle \mathbf{W}_i^{[l]}, \widehat{\xi}_l \rangle_\mathcal{H} +\epsilon_i = \left\langle \mathbf{W}_i, \sum \limits_{l=1}^L\widehat{\nu}_l \widehat{\boldsymbol{\zeta}}_l \right\rangle_\mathcal{H}+\epsilon_i,
\end{equation*}
which, given the uniqueness of $\boldsymbol{\eta}$, leads to
\begin{equation*}
	\widehat{\boldsymbol{\eta}} = \sum \limits_{l=1}^L\widehat{\nu}_l \widehat{\boldsymbol{\zeta}}_l.
\end{equation*}
Here, the number of PLS components $L$ to be estimated can be chosen by cross-validation.

@@

\subsection{Data Preprocessing} \label{subsec: Data Preprocessing}

Functional and scalar elements of the hybrid predictors often have incompatible units and/or exhibit different amounts of variation. This can be problematic for our PLS framework which is not scale invariant as: i) each predictor has different chance of contributing to the predictor/response structure; and ii) a predictor with high correlation to $Y$ but relatively low variance may be overlooked.

\section{Properties of the Proposed PLS Framework}
\label{sec: Properties of the Proposed PLS Framework}
\medskip
\noindent \textit{Orthonormality.}~
The constraint $\xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1$ enforces the following modified orthonormality of the estimated PLS components ($\widehat{\xi}_1, \widehat{\xi}_2, \ldots$)  based on the modified inner product $\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$ which now takes into account the roughness of the functions:
\begin{align*}
	\langle \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle \rangle 
	&= \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right \rangle_{L^2} \\
	&= \sum \limits_{k=1}^K \int_0^1 \widehat{\psi}_l^{(k)}(t_k) \widehat{\psi}_j^{(k)}(t_k) dt_k + \sum \limits_{r=1}^p \widehat{\theta}_{lr} \widehat{\theta}_{jr} + \sum_{k=1}^K \lambda_k \int_0^1 \ddot{\widehat{\psi}}_l^{(k)}(t_k) \ddot{\widehat{\psi}}_j^{(k)}(t_k) dt_k \\
	& = \mathbb{1}(l=j). 
\end{align*}
This modified orthonormality condition is one of the main geometric properties of the proposed PLS algorithm and is formally stated with proof in Section \ref{sec: Properties of the Proposed PLS Framework} (see Proposition \ref{proposition: modified orthnormality of PLS components}), along with other properties.

@@

\subsection{Tucker's Criterion}
We derive that the PLS components obtained from the first step of the proposed algorithm satisfy the Tucker's Criterion \citep{Tucker1938} extended to our scalar-on-hybrid regression model setting \eqref{eq: Hybrid functional model}. We omit $l$ in the notations and first define the cross-covariance terms between the response and predictors (observed versions if $l=1$ and residualized versions if $l \ge 2$): 
\begin{equation*}
	\begin{gathered}
		\sigma_{YX} = (\sigma_{YX}^{(1)}, \ldots, \sigma_{YX}^{(K)}) = (E(YX^{(1)}),\ldots, E(YX^{(K)})) = E(YX) \in \mathcal{F} \\
		\sigma_{YZ} = (\sigma_{YZ,1}, \ldots, \sigma_{YZ,p})^\top = (E(YZ_1),\ldots, E(YZ_p))^\top = E(Y\mathbf{Z}) \in \mathbb{R}^p \\
		\Sigma_{YW}=(\sigma_{YX}, \sigma_{YZ}) =  (E(YX), E(Y\mathbf{Z}))=E(Y\mathbf{W}) \in \mathcal{H}
	\end{gathered}
\end{equation*}
We also introduce two cross-covariance operators, $\mathcal{C}_{YW}=E(\mathbf{W} \otimes_\mathcal{H} Y): \mathcal{H} \rightarrow \mathbb{R}$ and $\mathcal{C}_{WY}=E(Y \otimes \mathbf{W}): \mathbb{R} \rightarrow \mathcal{H}$, which respectively map $h=(f, \mathbf{v}) \in \mathcal{H}$ to $\mathbb{R}$ and $d \in \mathbb{R}$ to $\mathcal{H}$ as follows:
\begin{align*}
	& \mathcal{C}_{YW} \mathbf{h} = E\{\langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H} Y \} = \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = \sum \limits_{k=1}^K \int_0^1 \sigma_{YX}^{(k)}(t_k) f^{(k)}(t_k) dt_k + E(Y \mathbf{Z}^\top) \mathbf{v} \\
	& \mathcal{C}_{WY} d = E (\langle Y, d \rangle \mathbf{W} ) = E(Y\mathbf{W})d =  \Sigma_{YW} \, d. 
\end{align*}

@@

\subsection{Geometric Properties}
In this section, we derive several geometric properties of the PLS components and and scores obtained from the proposed algorithm.

>>>>

%custom packages
 \usepackage{algorithm}
 \usepackage[noend]{algpseudocode}
 \usepackage{hyperref}
 \usepackage{enumerate}
 \usepackage{xcolor}
% \usepackage{url} % not crucial - just used below for the URL 
% \usepackage{bibunits}
\usepackage{subcaption}
% \usepackage{adjustbox}
\usepackage{verbatim} % to comment out

@@

% \usepackage{bm}
% \usepackage{multirow,multicol}
% \usepackage{verbatim}
% \usepackage{amsfonts,amssymb,amsthm,color,authblk}

% \definecolor{myblue}{RGB}{0, 0, 0}
% \newcommand{\blue}[1]{{\color{myblue}#1}}
\startlocaldefs
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% Uncomment next line to change            %%
%% the type of equation numbering           %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\numberwithin{equation}{section}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% For Axiom, Claim, Corollary, Hypothesis, %%
%% Lemma, Theorem, Proposition              %%
%% use \theoremstyle{plain}                 %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\theoremstyle{plain}
\newtheorem{axiom}{Axiom}
\newtheorem{claim}[axiom]{Claim}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% For Assumption, Definition, Example,     %%
%% Notation, Property, Remark, Fact         %%
%% use \theoremstyle{definition}            %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem*{example}{Example}
\newtheorem*{fact}{Fact}
\newtheorem{remark}{Remark}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Please put your definitions here:        %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand\numberthis{\addtocounter{equation}{1}\tag{\theequation}}
\newcommand{\jongmin}[1]{
	{ \color{teal} JM: #1}
}

@@

\section{Proposed PLS Algorithm} \label{sec: Proposed PLS Algorithm}
To address the limitations outlined in Section \ref{sec: Naive PLS Algorithm}, we propose  novel strategies for implementing the steps of the hybrid PLS algorithm. Our approach provides an efficient and robust means of producing PLS components and scores in the presence of multiple dense and/or irregular functional predictors and scalar predictors. It also incorporates a regularization scheme that enables the algorithm to borrow strength and exploit structural relationships within and between the functions to avoid overfitting of the PLS components and to improve the generalizability and interpretability of the predictive model.
Each iteration of our approach consists of two subroutines: regularized estimation of smoothed PLS components and orthogonalization, detailed in Sections~\ref{section:sub:compute_PLS_component} and~\ref{section:sub:residualization}, respectively. After a suitable number of iterations, the hybrid regression coefficient is estimated, as described in Section~\ref{section:sub:regression_coeff}. For notational simplicity, we omit the iteration index $l$ in the following discussion, with the understanding that the subroutines apply to any iteration. The complete algorithm is summarized in Algorithm~\ref{alg:main}.

\subsection{Preliminary step 1: finite-basis approximation}\label{sec: finite basis approximation}	

@@

\subsection{Preliminary step 2 : data preprocessing} \label{subsec: Data Preprocessing}
\jongmin{notation not changed yet}
Functional and scalar elements of the hybrid predictors often have incompatible units and/or exhibit different amounts of variation. This can be problematic for our PLS framework which is not scale invariant as: i) each predictor has different chance of contributing to the predictor/response structure; and ii) a predictor with high correlation to $Y$ but relatively low variance may be overlooked.

\subsection{Iterative steps}
The iterative process presented here yields an orthonormal hybrid basis that effectively captures the predictor-response relationships. It proceeds through two intermediate steps: the estimation of the PLS component direction (Section \ref{section:sub:compute_PLS_component}) and residualization (Section \ref{section:sub:residualization}). The properties of the resulting estimates are introduced in Section \ref{section:main:properties_of_our_method}.
\subsubsection{Iterative step 1: Regularized estimation of smoothed PLS component direction}  \label{section:sub:compute_PLS_component} 
We begin by formally introducing the core optimization problem pertinent to the PLS direction estimation, which is formulated as a generalized Rayleigh quotient (Proposition \ref{proposition:eigen_noregul}). Building upon this foundational concept, we present our regularized PLS component direction estimation step that promotes smoothness (Proposition \ref{proposition:eigen_regul}). Furthermore,  we detail an efficient computational scheme (Proposition \ref{proposition:linear_regul}).

\medskip
\noindent
\textit{Core optimization problem.}\label{sec: pls component computation intermediate}~
We   present the core optimization problem that directly estimates the hybrid PLS component direction. It fully leverages the continuous nature of the functional components and the function-scalar hybrid structure.
We describe the strategy at the $l$-th iteration. %For simplicity, we omit the iteration index and assume the observations have been residualized from previous steps (see Section~\ref{section:sub:residualization} for details). 
The  PLS component direction is estimated by the unit-norm direction $\xi^{[l]} \in \widetilde{\mathcal{H}}$ that maximizes the squared empirical covariance, which quantifies the linear dependence between the PLS scores $\langle \widetilde{W}_1, \xi \rangle_{\mathcal{H}}, \ldots, \langle \widetilde{W}_n, \xi \rangle_{\mathcal{H}}$ and the responses $y_1, \ldots, y_n$, defined as

@@

\medskip
\noindent
\textit{Proposed regularized estimation procedure.}~ \label{sec: Regularization of PLS Components}
Although Proposition \ref{proposition:eigen_noregul} efficiently estimates the PLS component direction $\hat{\xi} = (\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\zeta}})$, the functional components $\hat{\xi}_1, \ldots, \hat{\xi}_K$ may not be smooth, potentially leading to overfitting and unstable predictions. To address this, we propose a regularized extension that balances predictive performance with smoothness. Specifically, we penalize the roughness of each $\hat{\xi}_j$ using its integrated squared second derivative 
\begin{equation}\label{def:roughness_penalty}
	\operatorname{PEN}(\hat{\xi}_j) := \int_0^1 \bigl\{ \hat{\xi}_j^{\prime\prime}(t) \bigr\}^2 dt
	.
\end{equation}

@@

To avoid the orthogonal basis assumption of  \citet{Rice1991}, we adopt the strategy of \citet{Silverman1996}, which replaces the standard orthonormality constraint with a weaker one based on a modified inner product that incorporates roughness. Accordingly, our estimation procedure at the $l$-th iteration, iteration index omitted and assuming the observations have been residualized in previous steps, solves the following optimization problem:
\begin{equation}\label{def:maximizer_squared_empirical_cov_reg}
	\hat{\xi} 
	= 
	(\hat{\xi}_1, \ldots, \hat{\xi}_K, \hat{\boldsymbol{\zeta}}
	)
	:= \arg \max_{\xi \in \widetilde{\mathcal{H}}
	}~\widehat{\textnormal{Cov}}^2 
	\bigl(
	\langle \widetilde{W}, \xi \rangle_{\mathcal{H}}, Y 
	\bigr)~s.t.~\| \xi  \|_\mathcal{H} +  \sum \limits_{j=1}^K \lambda_j 
	\operatorname{PEN}(\xi_K) = 1.
\end{equation}
This formulation maximizes the squared covariance over a class of smooth functions.
Proposition~\ref{proposition:eigen_regul} expresses this problem as a generalized Rayleigh quotient.

@@

\subsubsection{Iterative step 2: residualization via hybrid-on-scalar regression} \label{section:sub:residualization}
The $l$-th iteration's second step involves residualization of both predictors and responses. We first compute the individual PLS score:  
\begin{equation}\label{def:plsscore}
	\hat{\rho}^{[l]}_i := \langle \widetilde{W}_i^{[l]}, \, \hat{\xi}^{[l]} \rangle_{\mathcal{H}},
\end{equation}
using the estimated PLS component direction $\widehat{\xi}^{[l]}$ obtained from Propositions \ref{proposition:eigen_regul} and \ref{proposition:linear_regul}. 
Since   $\widetilde{W}_i^{[l]}$ are assumed to have a sample mean of zero, these PLS scores will also have a sample mean of zero.
Using these PLS scores as scalar predictor observations, the $(l+1)$-th iteration's residualized response is computed as:
\begin{equation}\label{algorithm_step:residualization_response}
	Y_i^{[l+1]} := Y_i^{[l]} - 
	\frac{
		( \mathbf{y}^{[l]} )^\top  \hat{\boldsymbol{\rho}}^{[l]}
	}{
		( \hat{\boldsymbol{\rho}}^{[l]} )^\top  \hat{\boldsymbol{\rho}}^{[l]}
	}
	\widehat{\rho}_{il},
\end{equation}
which is equivalent to using the least squares estimate from regressing $Y_i^{[l]}$ on $\widehat{\rho}_{il}$,
a procedure identical to that found in the naive PLS algorithm (Section \ref{sec: Naive PLS Algorithm}). 
Since $Y_i^{[l]}$ are assumed to have a sample mean of zero, these residuals $Y_i^{[l+1]}$   also have a sample mean of zero.

@@

\begin{lemma}[Closed-form  solution]\label{proposition:closed_form_orthgonalization}
	Let us denote
	$
	\hat{\boldsymbol{\rho}}^{[l]} := (\hat{\rho}^{[l]}_1, \ldots, \hat{\rho}^{[l]}_n)^\top.
	%\quad\text{and} \quad		\bar{\rho}^{[l]} := (\hat{\boldsymbol{\rho}}^{[l]})^\top \hat{\boldsymbol{\rho}}^{[l]}.
	$
	The solution to the optimization problem \eqref{def:argmin_pensse}, denoted
	$\hat{\delta}^{[l]}   \in \tilde{\mathcal{H}}$, has basis coefficients
	\begin{equation*}
		\hat{\boldsymbol{\pi}}_j^{[l]}
		=
		\bigl(
		\| 	\hat{\boldsymbol{\rho}}^{[l]}\|_2^2
		B
		+
		\tau
		B^{\prime \prime}
		\bigr)^{-1}
		B
		(\Theta_j^{[l]})^\top
		\hat{\boldsymbol{\rho}}^{[l]}
		,
		~
		j = 1, \ldots, K,
	\end{equation*}
	  and scalar parts given by:
	 \begin{equation*}
	 	\hat{\boldsymbol{\chi} }^{[l]}
	 	=
	 	(\mathbf{Z}^{[l]})^\top  \hat{\boldsymbol{\rho}}^{[l]}.
	 \end{equation*}
\end{lemma}
Proof of Lemma \ref{proposition:closed_form_orthgonalization} is provided in Appendix \ref{section:proof:proposition:closed_form_orthgonalization}.

@@

\subsection{Final step: estimating  the hybrid regression coefficient}
\label{section:sub:regression_coeff}
\jongmin{notation not yet changed}
The regression coefficient $\boldsymbol{\eta}$ in model \eqref{eq: Hybrid functional model} can be written in terms of the estimated PLS components and scores. First, note that we can show $\widehat{\rho}_{il} = \langle \mathbf{W}_i^{[l]}, \widehat{\xi}_l \rangle_\mathcal{H} = \langle \mathbf{W}_i, \widehat{\boldsymbol{\zeta}}_l \rangle_\mathcal{H}$, where $\widehat{\boldsymbol{\zeta}}_l = \widehat{\xi}_l - \sum_{u=1}^{l-1} \langle \widehat{\boldsymbol{\delta}}_u, \widehat{\xi}_l \rangle_{\mathcal{H}} \widehat{\boldsymbol{\zeta}}_u$ for $l \ge 2$, with $\widehat{\boldsymbol{\zeta}}_1 = \widehat{\xi}_1$. Then, the decomposition of $Y_i$ in \eqref{eq: decomposition} leads to
\begin{equation*}
	Y_i = \sum \limits_{l=1}^L \widehat{\nu}_l \langle \mathbf{W}_i^{[l]}, \widehat{\xi}_l \rangle_\mathcal{H} +\epsilon_i = \left\langle \mathbf{W}_i, \sum \limits_{l=1}^L\widehat{\nu}_l \widehat{\boldsymbol{\zeta}}_l \right\rangle_\mathcal{H}+\epsilon_i,
\end{equation*}
which, given the uniqueness of $\boldsymbol{\eta}$, leads to
\begin{equation*}
	\widehat{\boldsymbol{\eta}} = \sum \limits_{l=1}^L\widehat{\nu}_l \widehat{\boldsymbol{\zeta}}_l.
\end{equation*}
Here, the number of PLS components $L$ to be estimated can be chosen by cross-validation.

@@

\section{Properties of the Proposed PLS Framework}
\label{section:main:properties_of_our_method}
\jongmin{notation not yet changed}

@@

\subsection{Tucker's Criterion}\jongmin{notation not yet changed}
We derive that the PLS components obtained from the first step of the proposed algorithm satisfy the Tucker's Criterion \citep{Tucker1938} extended to our scalar-on-hybrid regression model setting \eqref{eq: Hybrid functional model}. We omit $l$ in the notations and first define the cross-covariance terms between the response and predictors (observed versions if $l=1$ and residualized versions if $l \ge 2$): 
\begin{equation*}
	\begin{gathered}
		\sigma_{YX} = (\sigma_{YX}^{(1)}, \ldots, \sigma_{YX}^{(K)}) = (E(YX^{(1)}),\ldots, E(YX^{(K)})) = E(YX) \in \mathcal{F} \\
		\sigma_{YZ} = (\sigma_{YZ,1}, \ldots, \sigma_{YZ,p})^\top = (E(YZ_1),\ldots, E(YZ_p))^\top = E(Y\mathbf{Z}) \in \mathbb{R}^p \\
		\Sigma_{YW}=(\sigma_{YX}, \sigma_{YZ}) =  (E(YX), E(Y\mathbf{Z}))=E(Y\mathbf{W}) \in \mathcal{H}
	\end{gathered}
\end{equation*}
We also introduce two cross-covariance operators, $\mathcal{C}_{YW}=E(\mathbf{W} \otimes_\mathcal{H} Y): \mathcal{H} \rightarrow \mathbb{R}$ and $\mathcal{C}_{WY}=E(Y \otimes \mathbf{W}): \mathbb{R} \rightarrow \mathcal{H}$, which respectively map $h=(f, \mathbf{v}) \in \mathcal{H}$ to $\mathbb{R}$ and $d \in \mathbb{R}$ to $\mathcal{H}$ as follows:
\begin{align*}
	& \mathcal{C}_{YW} \mathbf{h} = E\{\langle \mathbf{W}, \mathbf{h} \rangle_\mathcal{H} Y \} = \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = \sum \limits_{k=1}^K \int_0^1 \sigma_{YX}^{(k)}(t_k) f^{(k)}(t_k) dt_k + E(Y \mathbf{Z}^\top) \mathbf{v} \\
	& \mathcal{C}_{WY} d = E (\langle Y, d \rangle \mathbf{W} ) = E(Y\mathbf{W})d =  \Sigma_{YW} \, d. 
\end{align*}

@@

\subsection{Geometric Properties}\jongmin{currently revising}
In this section, we derive several geometric properties of the PLS components and and scores obtained from the proposed algorithm.

\medskip
\noindent \textit{Orthonormality.}~
The constraint $\xi^{*\top} (J^\ast+\Lambda \ddot{J}^\ast) \xi^*=1$ enforces the following modified orthonormality of the estimated PLS components ($\widehat{\xi}_1, \widehat{\xi}_2, \ldots$)  based on the modified inner product $\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$ which now takes into account the roughness of the functions:
\begin{align*}
	\langle \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle \rangle 
	&= \langle \widehat{\xi}_l, \widehat{\xi}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right \rangle_{L^2} \\
	&= \sum \limits_{k=1}^K \int_0^1 \widehat{\psi}_l^{(k)}(t_k) \widehat{\psi}_j^{(k)}(t_k) dt_k + \sum \limits_{r=1}^p \widehat{\theta}_{lr} \widehat{\theta}_{jr} + \sum_{k=1}^K \lambda_k \int_0^1 \ddot{\widehat{\psi}}_l^{(k)}(t_k) \ddot{\widehat{\psi}}_j^{(k)}(t_k) dt_k \\
	& = \mathbb{1}(l=j). 
\end{align*}
This modified orthonormality condition is one of the main geometric properties of the proposed PLS algorithm and is formally stated with proof in Section \ref{section:main:properties_of_our_method} (see Proposition \ref{proposition: modified orthnormality of PLS components}), along with other properties.
